Report

### 2015-05-13 Lattice Reduction/Report April 2015/Report revised May 12 2015/Report_draft.tex
The final version 2nd revise

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}
\begin{document}
% make the title area
\begin{spacing}{2.5}
\maketitle
\section{Introduction}
Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems. Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems. Recently, an interesting property of large MIMO channel called channel hardening phenomenon has been found \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease. Simply saying, the channel "hardens". An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix becomes more and more ignorable comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.

 Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms. For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as multiplication and inverse. With channel hardening phenomenon, this process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}. Channel hardening phenomenon can also provide computational advances to machine learning based detectors, e.g. probability data association (PDA)\cite{fricke1900impact}\cite{pham2004generalized} and message passing detectors\cite{som2011low}\cite{goldberger2011mimo}\cite{lakshmi2013channel} and Monte-Carlo Markov Chain (MCMC) MIMO detectors\cite{farhang2006markov}\cite{datta2012novel}. This type of algorithms work well in large sparse systems.

>>>>

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}
\begin{document}
% make the title area
\begin{spacing}{2.5}
\maketitle
\section{Introduction}
Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems. Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems. Recently, an interesting property of large MIMO channel called channel hardening phenomenon has been found \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease. Simply saying, the channel "hardens". An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix become more and more negligible comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.

 Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms. For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as matrix multiplication and inverse. With channel hardening phenomenon, this process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}. Channel hardening phenomenon can also provide computational advances to machine learning based detectors, e.g. probability data association (PDA)\cite{fricke1900impact}\cite{pham2004generalized} and message passing detectors\cite{som2011low}\cite{goldberger2011mimo}\cite{lakshmi2013channel} and Monte-Carlo Markov Chain (MCMC) MIMO detectors\cite{farhang2006markov}\cite{datta2012novel}. This type of algorithms work well in large sparse systems.
